---
title: "Thymectomy"
author: "Oscar J. Ponce & Andrea Solis-Pazmino"
date: "5/7/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(dpi=900)
knitr::opts_chunk$set(dev='svg')

library("metafor")
library("tidyverse")
library("rmarkdown")
library("magrittr")
library("forestplot")
library(grid)
library(gt)
library(glue)

```

 
```{r cleaning, echo=FALSE, message=FALSE, warning=FALSE}
pao <- read.csv("Data/thymectomy_outcomes.csv")



names(pao)[1] <- "refid"
names(pao)[2] <- "int"
names(pao)[3] <- "comp"
names(pao)[4] <- "group"
names(pao)[5] <- "outcome"
names(pao)[6] <- "followup"
names(pao)[7] <- "totaln"
names(pao)[8:11] <- c("n1","n2","events1","events2")
names(pao)[12:14] <- c("eff", "cill", "ciul")
names(pao)[15] <- "pvalue"
names(pao)[16] <- "app"
pao <- pao[,-(17)]


pao$group[pao$group == "Overall "] <- "Overall"

pao$int[pao$int %in% c("extended transsternal\r\nthymectomies", 
                       "Extended Transternal thymectomy",
                       "extended transsternal\nthymectomies",
                       "Extended median sternotomy")] <- "ETsT"
pao$int[pao$int == "Infrasternal mediastinoscopic thymectomy (IMT)"] <- "IMT"
pao$int[pao$int == 
          "transcervical-subxiphoidvideothoracoscopic\n‘maximal’ thymectomy"] <- "TcSxVT"
pao$int[pao$int == "Transcervical thymectomy"] <- "BTcT"
pao$int[pao$int == "VATS unilateral alone"] <- 'VATS unilateral'
pao$int[pao$int == " VATET (bilateral)"] <- 'VATET bilateral'
pao$int[pao$int == " VATET (unilateral)"] <- 'VATET unilateral'
pao$int[pao$int == " VATS unilateral with robotic"] <- 'VATS unilateral with robotic'

pao$int[pao$int == "BTcT"] <- "T1a"
pao$int[pao$int == "VATS unilateral"] <- "T2a"
pao$int[pao$int == "VATS left"] <- "T2a left"
pao$int[pao$int == "VATET unilateral"] <- "T2b uni"
pao$int[pao$int == "VATET bilateral"] <- "T2b bi"
pao$int[pao$int == "VATS unilateral with robotic"] <- "T2c"
pao$int[pao$int == "ETsT"] <- "T3b"
pao$int[pao$int == "TcSxVT"] <- "T5a"
pao$int[pao$int == "IMT"] <- "T5d"


pao$comp[pao$comp %in% c("Extended median sternotomy", 
                         "Extended Transternal thymectomy")] <- "ETsT"
pao$comp[pao$comp %in% 
           c("\ntranscervical-subxiphoidvideothoracoscopic\n‘maximal’ thymectomy",
             "transcervical-subxiphoidvideothoracoscopic\n‘maximal’ thymectomy", 
             "transcervical-subxiphoidvideothoracoscopic\n‘maximal’ thymectomy\n")] <- "TcSxVT"
pao$comp[pao$comp == "basic transsternal\nthymectomies"] <- "STsT"
pao$comp[pao$comp == "VATS unilateral alone"] <- 'VATS unilateral'
pao$comp[pao$comp == " VATET (bilateral)"] <- 'VATET bilateral'
pao$comp[pao$comp == " VATS unilateral with robotic"] <- 'VATS unilateral with robotic'
pao$comp[pao$comp == "Anterolateral thoracotomy"] <- 'STsT'


pao$comp[pao$comp == "BTcT"] <- "T1a"
pao$comp[pao$comp == "VATS unilateral"] <- "T2a"
pao$comp[pao$comp == "VATS right"] <- "T2a right"
pao$comp[pao$comp == "VATET bilateral"] <- "T2b bi"
pao$comp[pao$comp == "VATS unilateral with robotic"] <- "T2c"
pao$comp[pao$comp == "STsT"] <- "T3a"
pao$comp[pao$comp == "ETsT"] <- "T3b"
pao$comp[pao$comp == "TcSxVT"] <- "T5a"



pao <- pao[c(1:62,66:67,63:65),]
row.names(pao) <- c(1:67)


#Changin direction of comparison for better interpretation
pao[63,] <- pao[63,c(1, 3, 2, 4:7, 9, 8, 11, 10,12:16)]
pao[c(43,46,49),] <- pao[c(43,46,49),c(1, 3, 2, 4:7, 9, 8, 11, 10,12:16)]


#round fucntion
round2 = function(x, n=0) {scale<-10^n; sign(x)*trunc(abs(x)*scale+0.5)/scale}
pao$events1 <- round2(pao$events1, 0)
pao$events2 <- round2(pao$events2, 0)


#creating author name based on refID
pao$author <- 
  ifelse(pao$refid==60, paste("Siwachat et al., 2016"),
  ifelse(pao$refid==130, paste("Xie et al., 2016"),
  ifelse(pao$refid==196, paste("Liu et al., 2015"),
  ifelse(pao$refid==257, paste("Chen et al., 2014"),
  ifelse(pao$refid==282, paste("Liu et al., 2013"),
  ifelse(pao$refid==340, paste("Huang et al., 2011"),
  ifelse(pao$refid==342, paste("Rucket et al., 2011"),
  ifelse(pao$refid==366, paste("Zielinski et al., 2010"),
  ifelse(pao$refid==377, paste("Lin et al., 2010"),
  ifelse(pao$refid==390, paste("Murai et al., 2009"),
  ifelse(pao$refid==592, paste("Zielinski et al., 2004"),
  ifelse(pao$refid==635, paste("Mantegazza et al., 2003"),
  ifelse(pao$refid==642, paste("Ruckert et al., 2003"),
  ifelse(pao$refid==1424, paste("Tomulescu et al., 2016"),
  ifelse(pao$refid==2416, paste("INCMNSZ, 2019"), NA )))))))))))))))

#Exclude RefID 592 because it enrolled patients that were enrolled for 366 
pao <- pao[!(pao$refid %in% 592),]
pao <- pao[!(pao$refid %in% 635),]


#Additional modifications
pao$int[pao$int == "T2a left"] <- "T2b left"

pao$comp[pao$comp == "T2a right"] <- "T2b right"
pao$int[pao$int == "T2b uni"] <- "T2b"

pao$comp[pao$comp == "T2b bi"] <- "T2b"
pao$int[pao$int == "T2b bi"] <- "T2b"


pao$comp[pao$comp == "T2a"] <- "T2b"
pao$int[pao$int == "T2a"] <- "T2b"

pao$comp <- ifelse(pao$refid==196, paste("T2b bi"), pao$comp)
pao$int <- ifelse(pao$refid==196, paste("T2b uni"), pao$int)



#Final paste
pao$comparison <- paste(pao$int, " vs. ", pao$comp)



```








## Open Data
>Click any of the following links to view the documents



| Stage  |      File     |  
|:----------:|:-------------:|
| Protocol | [Prospero](https://www.crd.york.ac.uk/prospero/display_record.php?RecordID=166827)|
| Search strategy | `Available in this page` |
| Abstract screening | [References used in this stage or search results](https://github.com/ponceoscarj/Thymectomy/blob/master/Screening_results/articles_for_abstract_screening.txt) |
| Full-text screening | [References used in this stage](https://github.com/ponceoscarj/Thymectomy/blob/master/Screening_results/articles_for_fulltext_screening.txt) |
| Included studies | [References used for data extraction](https://github.com/ponceoscarj/Thymectomy/blob/master/Screening_results/included_articles.txt) |
| Raw data | [Data as `.CSV`](https://github.com/ponceoscarj/Thymectomy/blob/master/Data/thymectomy_outcomes.csv)|
| Analysis codes | [Script as `R Markdown`](https://github.com/ponceoscarj/Thymectomy/blob/master/Thymectomy_results.Rmd)|


## Search strategy


<details>
<summary>Show OVID search</summary>

```{r ovid, echo=FALSE}
ovid <- read.csv("1 Search strategy/ovid_search.csv")
names(ovid)[1] <- "line"
names(ovid)[2] <- "terms"

ovid <- as_tibble(ovid)

ovid %>% 
gt() %>%
  tab_header( 
    title = md("**Ovid Search**"),
    subtitle = "Databases: EBM Reviews - Cochrane Central Register of Controlled Trials April 2019, EBM Reviews - Cochrane Database of Systematic Reviews 2005 to May 2, 2019, Embase 1974 to 2019 May 03, Ovid MEDLINE(R) and Epub Ahead of Print, In-Process & Other Non-Indexed Citations and Daily 1946 to May 03, 2019") %>%
  cols_align(
    align = "left",
    columns = TRUE
  ) %>%
  fmt_number( 
    columns = vars("line"),
    decimals = 0
  ) %>%
  fmt_passthrough(
    columns = vars("terms"),
  ) %>%

  cols_label(
    line = md("**Search <br> line**"),
    terms = md("**Search <br> terms**")
  ) %>%
  tab_options(
        column_labels.border.bottom.width = 0.5,
        column_labels.border.top.width = 0.5,
        table.font.size = "small",

        data_row.padding = px(5)
  )


```

</details>


<details>
<summary>Show SCOPUS search</summary>

```{r scopus, echo=FALSE}
scopus <- read.csv("1 Search strategy/scopus_search.csv")
names(scopus)[1] <- "line"
names(scopus)[2] <- "terms"

ovid <- as_tibble(scopus)

scopus %>% 
gt() %>%
  tab_header( 
    title = md("**Scopus Search**"),
  ) %>%
  cols_align(
    align = "left",
    columns = TRUE
  ) %>%
  fmt_number( 
    columns = vars("line"),
    decimals = 0
  ) %>%
  fmt_passthrough(
    columns = vars("terms"),
  ) %>%
  cols_label(
    line = md("**Search <br> line**"),
    terms = md("**Search <br> terms**"),
  ) %>%
  tab_options(
        column_labels.border.bottom.width = 0.5,
        data_row.padding = px(4)
  )%>%
  tab_options(
        column_labels.border.bottom.width = 0.5,
        column_labels.border.top.width = 0.5,
        table.font.size = "small",

        data_row.padding = px(5)
  )

```
</details>



```{r overall_analysis, echo=FALSE}
prema1 <- escalc(measure="RR",ai=events1, ci=events2, n1i=n1, n2i=n2,
                  subset=(followup==3 & 
                            comparison=="T3b  vs.  T3a"), data=pao)
prema1 <- summary(prema1)
prema1$rr <- paste(formatC((exp(prema1$yi)), format='f', digits=2), " ",
                    "(", formatC((exp(prema1$ci.lb)), format='f', digits=2), "-",
                    formatC((exp(prema1$ci.ub)), format='f', digits=2),")")
ma1 <- rma(measure="RR", yi,vi, data=prema1, method="REML")
expma1 <- predict(ma1, transf = transf.exp.int)


prema2 <- escalc(measure="RR",ai=events1, ci=events2, n1i=n1, n2i=n2,
                  subset=(followup==4 & 
                            comparison=="T3b  vs.  T3a"), data=pao)
prema2 <- summary(prema2)
prema2$rr <- paste(formatC((exp(prema2$yi)), format='f', digits=2), " ",
                    "(", formatC((exp(prema2$ci.lb)), format='f', digits=2), "-",
                    formatC((exp(prema2$ci.ub)), format='f', digits=2),")")
ma2 <- rma(measure="RR", yi,vi, data=prema2, method="REML")
expma2 <- predict(ma2, transf = transf.exp.int)



prema3 <- escalc(measure="RR",ai=events1, ci=events2, n1i=n1, n2i=n2,
                  subset=(followup==5 & 
                            comparison=="T3b  vs.  T3a"), data=pao)
prema3 <- summary(prema3)
prema3$rr <- paste(formatC((exp(prema3$yi)), format='f', digits=2), " ",
                    "(", formatC((exp(prema3$ci.lb)), format='f', digits=2), "-",
                    formatC((exp(prema3$ci.ub)), format='f', digits=2),")")
ma3 <- rma(measure="RR", yi,vi, data=prema3, method="REML")
expma3 <- predict(ma3, transf = transf.exp.int)



ma4 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==10 & comparison=="T1a  vs.  T3b"),
            method="REML")
expma4 <- predict(ma4, transf = exp, digits=2)


ma5 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
           data=pao, subset=(followup==3 & comparison=="T2b  vs.  T3a"), 
           method="REML")
expma5 <- predict(ma5, transf = exp, digits=2)


ma6 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
           data=pao, subset=(followup==4 & comparison=="T2b  vs.  T3a"), 
           method="REML")
expma6<- predict(ma6, transf = exp, digits=2)


ma7 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
           data=pao, subset=(followup==5 & comparison=="T2b  vs.  T3a"),
           method="REML")
expma7 <- predict(ma7, transf = exp, digits=2)


prema8 <- escalc(measure="RR",ai=events1, ci=events2, n1i=n1, n2i=n2,
                  subset=(followup==3 & 
                            comparison=="T2b  vs.  T3b" & group=="Overall"), data=pao)
prema8 <- summary(prema8)
prema8$rr <- paste(formatC((exp(prema8$yi)), format='f', digits=2), " ",
                    "(", formatC((exp(prema8$ci.lb)), format='f', digits=2), "-",
                    formatC((exp(prema8$ci.ub)), format='f', digits=2),")")
ma8 <- rma(measure="RR", yi,vi, data=prema8, method="REML")
expma8 <- predict(ma8, transf = transf.exp.int)


prema9 <- escalc(measure="RR",ai=events1, ci=events2, n1i=n1, n2i=n2,
                  subset=(followup==4 & 
                            comparison=="T2b  vs.  T3b" & group=="Overall"), data=pao)
prema9 <- summary(prema9)
prema9$rr <- paste(formatC((exp(prema9$yi)), format='f', digits=2), " ",
                    "(", formatC((exp(prema9$ci.lb)), format='f', digits=2), "-",
                    formatC((exp(prema9$ci.ub)), format='f', digits=2),")")
ma9 <- rma(measure="RR", yi,vi, data=prema9, method="REML")
expma9 <- predict(ma9, transf = transf.exp.int)


prema10 <- escalc(measure="RR",ai=events1, ci=events2, n1i=n1, n2i=n2,
                  subset=(followup==5 & 
                            comparison=="T2b  vs.  T3b" & group=="Overall"), data=pao)
prema10 <- summary(prema10)
prema10$rr <- paste(formatC((exp(prema10$yi)), format='f', digits=2), " ",
                    "(", formatC((exp(prema10$ci.lb)), format='f', digits=2), "-",
                    formatC((exp(prema10$ci.ub)), format='f', digits=2),")")
ma10 <- rma(measure="RR", yi,vi, data=prema10, method="REML")
expma10 <- predict(ma10, transf = transf.exp.int)


prema11 <- escalc(measure="RR",ai=events1, ci=events2, n1i=n1, n2i=n2,
                  subset=(followup==6 & 
                            comparison=="T2b  vs.  T3b" & group=="Overall"), data=pao)
prema11 <- summary(prema11)
prema11$rr <- paste(formatC((exp(prema11$yi)), format='f', digits=2), " ",
                    "(", formatC((exp(prema11$ci.lb)), format='f', digits=2), "-",
                    formatC((exp(prema11$ci.ub)), format='f', digits=2),")")
ma11 <- rma(measure="RR", yi,vi, data=prema11, method="REML")
expma11 <- predict(ma11, transf = transf.exp.int)


prema12 <- escalc(measure="RR",ai=events1, ci=events2, n1i=n1, n2i=n2,
                  subset=(followup==7 & 
                            comparison=="T2b  vs.  T3b" & group=="Overall"), data=pao)
prema12 <- summary(prema12)
prema12$rr <- paste(formatC((exp(prema12$yi)), format='f', digits=2), " ",
                    "(", formatC((exp(prema12$ci.lb)), format='f', digits=2), "-",
                    formatC((exp(prema12$ci.ub)), format='f', digits=2),")")
ma12 <- rma(measure="RR", yi,vi, data=prema12, method="REML")
expma12 <- predict(ma12, transf = transf.exp.int)


prema13 <- escalc(measure="RR",ai=events1, ci=events2, n1i=n1, n2i=n2,
                  subset=(followup==8 & 
                            comparison=="T2b  vs.  T3b" & group=="Overall"), data=pao)
prema13 <- summary(prema13)
prema13$rr <- paste(formatC((exp(prema13$yi)), format='f', digits=2), " ",
                    "(", formatC((exp(prema13$ci.lb)), format='f', digits=2), "-",
                    formatC((exp(prema13$ci.ub)), format='f', digits=2),")")
ma13 <- rma(measure="RR", yi,vi, data=prema13, method="REML")
expma13 <- predict(ma13, transf = transf.exp.int)



ma14 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==9 & 
                                comparison=="T2b  vs.  T3b"),
            method="REML")
expma14 <- predict(ma14, transf = exp, digits=2)


ma24 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==3 & 
                                comparison=="T2b uni  vs.  T2b bi"),
            method="REML")
expma24 <- predict(ma24, transf = exp, digits=2)


ma25 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==4 & 
                                comparison=="T2b uni  vs.  T2b bi"),
            method="REML")
expma25 <- predict(ma25, transf = exp, digits=2)


ma26 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==5 & 
                                comparison=="T2b uni  vs.  T2b bi"),
            method="REML")
expma26 <- predict(ma26, transf = exp, digits=2)


ma27 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==6 & 
                                comparison=="T2b uni  vs.  T2b bi"),
            method="REML")
expma27 <- predict(ma27, transf = exp, digits=2)

ma28 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==3 & comparison=="T2b left  vs.  T2b right"),
            method="REML")
expma28 <- predict(ma28, transf = exp, digits=2)


ma29 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==4 & comparison=="T2b left  vs.  T2b right"),
            method="REML")
expma29 <- predict(ma29, transf = exp, digits=2)


ma30 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==3 & 
                                comparison=="T2c  vs.  T2b"),
            method="REML")
expma30 <- predict(ma30, transf = exp, digits=2)


ma31 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==5 & 
                                comparison=="T2c  vs.  T2b"),
            method="REML")
expma31 <- predict(ma31, transf = exp, digits=2)



ma32 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
           data=pao, subset=(followup==3 & comparison=="T5a  vs.  T3a"),
           method="REML")
expma32 <- predict(ma32, transf = exp, digits=2)


ma33 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
           data=pao, subset=(followup==4 & comparison=="T5a  vs.  T3a"), 
           method="REML")
expma33 <- predict(ma33, transf = exp, digits=2)


ma34 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
           data=pao, subset=(followup==5 & comparison=="T5a  vs.  T3a"), 
           method="REML")
expma34 <-predict(ma34, transf = exp, digits=2)


ma35 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
           data=pao, subset=(followup==3 & comparison=="T5a  vs.  T3b"),
           method="REML")
expma35 <- predict(ma35, transf = exp, digits=2)


ma36 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
           data=pao, subset=(followup==4 & comparison=="T5a  vs.  T3b"), 
           method="REML")
expma36 <- predict(ma36, transf = exp, digits=2)


ma37 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
           data=pao, subset=(followup==5 & comparison=="T5a  vs.  T3b"), 
           method="REML")
expma37 <- predict(ma37, transf = exp, digits=2)


ma38 <- rma(measure="RR", ai=events1, ci=events2, n1i=n1, n2i=n2, 
            data=pao, subset=(followup==5 & comparison=="T5d  vs.  T3b"), 
            method="REML")
expma38 <- predict(ma38, transf = exp, digits=2)
```



```{r organization_summary, echo=FALSE}
head <- c("comparison",  "followup", "k", "ai", "bi",
                     "ci", "di", "i2", "eff", "llci", "ulci","p")

a<- rbind(
  c("T3b  vs.  T3a",  "3 years",  ma1[[15]], 
  sum(prema1$events1), (sum(prema1$n1)-sum(prema1$events1)),
  sum(prema1$events2), (sum(prema1$n2)-sum(prema1$events2)), 
  ma1[[25]], expma1[[1]], expma1[[3]],
  expma1[[4]], ma1[[24]] ), 
  c("T3b  vs.  T3a",  "4 years", ma2[[15]], 
  sum(prema2$events1), (sum(prema2$n1)-sum(prema2$events1)),
  sum(prema2$events2), (sum(prema2$n2)-sum(prema2$events2)), 
  ma2[[25]], expma2[[1]], expma2[[3]],
  expma2[[4]], ma2[[24]]), 
  c("T3b  vs.  T3a", "5 years", ma3[[15]], 
  sum(prema3$events1), (sum(prema3$n1)-sum(prema3$events1)),
  sum(prema3$events2), (sum(prema3$n2)-sum(prema3$events2)), 
  ma3[[25]], expma3[[1]], expma3[[3]],
  expma3[[4]], ma3[[24]]))




b <-  c("T1a  vs.  T3b",  "10 years", ma4[[15]], sum(ma4[[42]]), sum(ma4[[43]]),
    sum(ma4[[44]]),sum(ma4[[45]]), ma4[[25]], expma4[[1]], expma4[[3]], expma4[[4]],
    ma4[[24]])



c <- rbind(
  c("T2b  vs.  T3a",  "3 years", ma5[[15]], sum(ma5[[42]]), sum(ma5[[43]]),
    sum(ma5[[44]]),sum(ma5[[45]]), ma5[[25]], expma5[[1]], expma5[[3]], expma5[[4]],
    ma5[[24]]), 
  c("T2b  vs.  T3a",  "4 years", ma6[[15]], sum(ma6[[42]]), sum(ma6[[43]]),
    sum(ma6[[44]]),sum(ma6[[45]]), ma6[[25]], expma6[[1]], expma6[[3]], expma6[[4]],
    ma6[[24]]),
  c("T2b  vs.  T3a", "5 years", ma7[[15]], sum(ma7[[42]]), sum(ma7[[43]]),
    sum(ma7[[44]]),sum(ma7[[45]]), ma7[[25]], expma7[[1]], expma7[[3]], expma7[[4]],
    ma7[[24]]))
  

d <- rbind(
  c("T2b  vs.  T3b", "3 years", ma8[[15]], 
  sum(prema8$events1), (sum(prema8$n1)-sum(prema8$events1)),
  sum(prema8$events2), (sum(prema8$n2)-sum(prema8$events2)), 
  ma8[[25]], expma8[[1]], expma8[[3]],
  expma8[[4]], ma8[[24]]),
  c("T2b  vs.  T3b", "4 years", ma9[[15]], 
    sum(prema9$events1), (sum(prema9$n1)-sum(prema9$events1)),
    sum(prema9$events2), (sum(prema9$n2)-sum(prema9$events2)), 
    ma9[[25]], expma9[[1]], expma9[[3]],
    expma9[[4]], ma9[[24]]),
  c("T2b  vs.  T3b", "5 years", ma10[[15]], 
    sum(prema10$events1), (sum(prema10$n1)-sum(prema10$events1)),
    sum(prema10$events2), (sum(prema10$n2)-sum(prema10$events2)), 
    ma10[[25]], expma10[[1]], expma10[[3]],
    expma10[[4]], ma10[[24]]),
  c("T2b  vs.  T3b", "6 years", ma11[[15]], 
    sum(prema11$events1), (sum(prema11$n1)-sum(prema11$events1)),
    sum(prema11$events2), (sum(prema11$n2)-sum(prema11$events2)), 
    ma11[[25]], expma11[[1]], expma11[[3]],
    expma11[[4]], ma11[[24]]),
  c("T2b  vs.  T3b", "7 years", ma12[[15]], 
    sum(prema12$events1), (sum(prema12$n1)-sum(prema12$events1)),
    sum(prema12$events2), (sum(prema12$n2)-sum(prema12$events2)), 
    ma12[[25]], expma12[[1]], expma12[[3]],
    expma12[[4]], ma12[[24]]),
  c("T2b  vs.  T3b", "8 years", ma13[[15]], 
    sum(prema13$events1), (sum(prema13$n1)-sum(prema13$events1)),
    sum(prema13$events2), (sum(prema13$n2)-sum(prema13$events2)), 
    ma13[[25]], expma13[[1]], expma13[[3]],
    expma13[[4]], ma13[[24]]),
  c("T2b  vs.  T3b", "9 years", ma14[[15]], sum(ma14[[42]]), sum(ma14[[43]]),
    sum(ma14[[44]]),sum(ma14[[45]]), ma14[[25]], expma14[[1]], expma14[[3]],
    expma14[[4]], ma14[[24]]))




g <- rbind(
  c("T2b uni  vs.  T2b bi", "3 years", ma24[[15]], sum(ma24[[42]]), sum(ma24[[43]]),
    sum(ma24[[44]]),sum(ma24[[45]]), ma24[[25]], expma24[[1]], expma24[[3]],
    expma24[[4]], ma24[[24]]),
  c("T2b uni  vs.  T2b bi", "4 years", ma25[[15]], sum(ma25[[42]]), sum(ma25[[43]]),
    sum(ma25[[44]]),sum(ma25[[45]]), ma25[[25]], expma25[[1]], expma25[[3]],
    expma25[[4]], ma25[[24]]),
  c("T2b uni  vs.  T2b bi", "5 years", ma26[[15]], sum(ma26[[42]]), sum(ma26[[43]]),
    sum(ma26[[44]]),sum(ma26[[45]]), ma26[[25]], expma26[[1]], expma26[[3]],
    expma26[[4]], ma26[[24]]),
  c("T2b uni  vs.  T2b bi", "6 years", ma27[[15]], sum(ma27[[42]]), sum(ma27[[43]]),
    sum(ma27[[44]]),sum(ma27[[45]]), ma27[[25]], expma27[[1]], expma27[[3]],
    expma27[[4]], ma27[[24]]))




h <- rbind(
  c("T2b left  vs.  T2b right", "3 years", ma28[[15]], sum(ma28[[42]]), 
    sum(ma28[[43]]), sum(ma28[[44]]),sum(ma28[[45]]), ma28[[25]], expma28[[1]], 
    expma28[[3]], expma28[[4]], ma28[[24]]),
  c("T2b left  vs.  T2b right", "4 years", ma29[[15]], sum(ma29[[42]]),
    sum(ma29[[43]]), sum(ma29[[44]]),sum(ma29[[45]]), ma29[[25]], expma29[[1]],
    expma29[[3]], expma29[[4]], ma29[[24]]))

i <- rbind(
  c("T2c  vs.  T2b", "3 years", ma30[[15]], sum(ma30[[42]]),
    sum(ma30[[43]]), sum(ma30[[44]]),sum(ma30[[45]]), ma30[[25]], expma30[[1]],
    expma30[[3]], expma30[[4]], ma30[[24]]),
  c("T2c  vs.  T2b", "5 years", ma31[[15]], sum(ma31[[42]]),
    sum(ma31[[43]]), sum(ma31[[44]]),sum(ma31[[45]]), ma31[[25]], expma31[[1]],
    expma31[[3]], expma31[[4]], ma31[[24]]))


j <- rbind(
  c("T5a  vs.  T3a", "3 years", ma32[[15]], sum(ma32[[42]]), sum(ma32[[43]]),
    sum(ma32[[44]]),sum(ma32[[45]]), ma32[[25]], expma32[[1]], expma32[[3]], expma32[[4]],
    ma32[[24]]),
  c("T5a  vs.  T3a", "4 years", ma33[[15]], sum(ma33[[42]]), sum(ma33[[43]]),
    sum(ma33[[44]]),sum(ma33[[45]]), ma33[[25]], expma33[[1]], expma33[[3]], expma33[[4]],
    ma33[[24]]), 
  c("T5a  vs.  T3a", "5 years", ma34[[15]], sum(ma34[[42]]), sum(ma34[[43]]),
    sum(ma34[[44]]),sum(ma34[[45]]), ma34[[25]], expma34[[1]], expma34[[3]], expma34[[4]],
    ma34[[24]]))


k <- rbind(
  c("T5a  vs.  T3b", "3 years", ma35[[15]], sum(ma35[[42]]), sum(ma35[[43]]),
    sum(ma35[[44]]),sum(ma35[[45]]), ma35[[25]], expma35[[1]], expma35[[3]], expma35[[4]],
    ma35[[24]]),
  c("T5a  vs.  T3b", "4 years", ma36[[15]], sum(ma36[[42]]), sum(ma36[[43]]),
    sum(ma36[[44]]),sum(ma36[[45]]), ma36[[25]], expma36[[1]], expma36[[3]], expma36[[4]],
    ma36[[24]]), 
  c("T5a  vs.  T3b", "5 years", ma37[[15]], sum(ma37[[42]]), sum(ma37[[43]]),
    sum(ma37[[44]]),sum(ma37[[45]]), ma37[[25]], expma37[[1]], expma37[[3]], expma37[[4]],
    ma37[[24]]))

l <- c("T5d  vs.  T3b", "5 years", ma38[[15]], sum(ma38[[42]]), sum(ma38[[43]]),
    sum(ma38[[44]]),sum(ma38[[45]]), ma38[[25]], expma38[[1]], expma38[[3]], 
    expma38[[4]], ma38[[24]])



summarybefore <- rbind(
  c("a", "T3b  vs.  T3a"),
  c("b", "T3b  vs.  T1a"),
  c("c", "T3a  vs.  T2b"),
  c("d", "T3b  vs.  T2b"),
  c("g", "T2b uni  vs.  T2b bi"),
  c("h", "T2b left  vs.  T2b right"),
  c("i", "T2c  vs.  T2b"),
  c("j", "T3a  vs.  T5a"),
  c("k", "T3b  vs.  T5a"),
  c("l", "T3b  vs.  T5d"))

summaryafter <- rbind(
  c("a", "T3b  vs.  T3a"),
  c("b", "T1a  vs.  T3b"),
  c("c", "T2b  vs.  T3a"),
  c("d", "T2b  vs.  T3b"),
  c("g", "T2b uni  vs.  T2b bi"),
  c("h", "T2b left  vs.  T2b right"),
  c("i", "T2c  vs.  T2b"),
  c("j", "T5a  vs.  T3a"),
  c("k", "T5a  vs.  T3b"),
  c("l", "T5d  vs.  T3b"))


```



## Summary of forest plots

### Figure 1 
<details><summary>Click to show</summary>

*Risk of achieving Complete Stable Remission in patients with myasthenia gravis who underwent* ***Transsternal thymectomy***  *vs.*  ***Transsternal thymectomy*** *at different follow-ups*

```{r,  fig.height=3, fig.width=13, echo=FALSE, message=FALSE, warning=FALSE}
agr <- as_tibble(a)
colnames(agr) <- head
agr[,c(3:7,8:12)] <- sapply(agr[,c(3:7,8:12)], as.numeric)
agr$i2 <- ifelse(agr$k==1, "na", formatC(round2(agr$i2), format='f', digits=0))
agr$rr <- paste(formatC(round2(agr$eff, n=2), format='f', digits=2), 
                "(", formatC(round2(agr$llci, n=2), format='f', digits=2),
                "-", formatC(round2(agr$ulci, n=2), format='f', digits=2),
                ")")
agr$n1 <- (agr$ai + agr$bi)
agr$n2 <- (agr$ci + agr$di)
agr$rate1 <- paste(agr$ai,"/",agr$n1)
agr$rate2 <- paste(agr$ci,"/",agr$n2)


agr$p2 <- 
  ifelse(is.na(agr$p), NA, 
  ifelse(agr$p<0.001, paste("<0.001"), 
         paste(formatC(round2(agr$p,n=3), format='f', digits=3))))


agr <- agr %>% add_row(followup="Extended Transsternal vs. Standard Transsternal", .before = 1)
agr <- agr %>% add_row(.before =  1)
agr <- agr %>% add_row(.after =  5)


agr2 <- cbind(c("Treatment vs. Control", "Follow-up",agr$followup),
              c("N of studies", NA, agr$k),
              c("Treatment", "events/n", agr$rate1),
              c("Control", "events/n", agr$rate2),
              c("I^2", NA, agr$i2),
              c("Relative Risk (95% CI)", NA, agr$rr),
              c("p value", NA, agr$p2))
sub1 <- c(5:7)
agr2[,1][sub1] <- paste("  ",agr2[,1][sub1])

rrsagr <- structure(list(
  mean = c(NA, NA, agr$eff),
  lower = c(NA, NA, agr$llci),
  upper = c(NA, NA, agr$ulci)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -6L),
  class = "data.frame")

forestplot(agr2,
           rrsagr,
           graph.pos = 6,
           zero=1,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:8), col="black")),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           is.summary = c(T, T, F, 
                          T, rep(F, 3), F),
           align = c("l","c", "c", "c", "l", "l", "l"),
           boxsize = 0.5,
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                            ticks = gpar(cex = 0.9, fontface="bold"),
                            summary = gpar(cex = 0.9),
                            xlab = gpar(cex=0.9)),
           xticks = c(0.12, 0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(7,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))

```

> To generate this forest plot, we used information from Supplementary Figures 1 to 3.

</details>


### Figure 2
<details><summary>Click to show</summary>

*Risk of achieving Complete Stable Remission in patients with myasthenia gravis who underwent* ***Transsternal  Thymectomy*** *vs.* ***Minimally Invasive Thymectomy*** *at different follow-ups*
```{r, fig.height=7, fig.width=19, echo=FALSE, message=FALSE, warning=FALSE}
lessagr <- as_tibble(rbind(b, c, d, j, k, l))
colnames(lessagr) <- head

lessagr[,c(3:8,9:12)] <- sapply(lessagr[,c(3:8,9:12)], as.numeric)
lessagr$i2 <- ifelse(lessagr$k==1, "na", 
                     paste(formatC(round2(lessagr$i2,n=0), format='f',digits=0), "%"))
lessagr$rr <- paste(formatC(round2(lessagr$eff, n=2), format='f', digits=2), 
                "(", formatC(round2(lessagr$llci, n=2), format='f', digits=2),
                "-", formatC(round2(lessagr$ulci, n=2), format='f', digits=2),
                ")")
lessagr$n1 <- (lessagr$ai + lessagr$bi)
lessagr$n2 <- (lessagr$ci + lessagr$di)
lessagr$rate1 <- paste(lessagr$ai,"/",lessagr$n1)
lessagr$rate2 <- paste(lessagr$ci,"/",lessagr$n2)
lessagr$p2 <- 
  ifelse(is.na(lessagr$p), NA, 
  ifelse(lessagr$p<0.001, paste("<0.001"), 
         paste(formatC(round2(lessagr$p,n=3), format='f', digits=3))))


lessagr <- lessagr %>% add_row(followup="Basic Transcervical vs. Extended Transsternal", .before = 1)
lessagr <- lessagr %>% add_row(followup="VATS extended vs. Standard Transsternal ", .before = 3)
lessagr <- lessagr %>% add_row(followup="VATS extended vs. Extended Transsternal", .before = 7)
lessagr <- lessagr %>% add_row(followup="Transcervical-Subxiphoid vs. Standard Transsternal", .before = 15)
lessagr <- lessagr %>% add_row(followup="Extended Transsternal vs. Transcervical-Subxiphoid", .before = 19)
lessagr <- lessagr %>% add_row(followup="Subxiphoid Mediastinoscopy vs. Extended Transsternal", .before = 23)

lessagr <- lessagr %>% add_row(.before = 1)
lessagr <- lessagr %>% add_row(.after = 25)


lessagr2 <- cbind(c("Treatment vs. Control", "Follow-up",lessagr$followup),
              c("N of studies", NA, lessagr$k),
              c("Treatment", "events/n", lessagr$rate1),
              c("Control", "events/n", lessagr$rate2),
              c("I^2", NA, lessagr$i2),
              c("Relative Risk (95% CI)", NA, lessagr$rr),
              c("p value", NA, lessagr$p2))


sub1 <- c(5, 7:9, 11:17, 19:21, 23:25, 27)
lessagr2[,1][sub1] <- paste("  ",lessagr2[,1][sub1])

rrslessagr <- structure(list(
  mean = c(NA, NA, lessagr$eff),
  lower = c(NA, NA, lessagr$llci),
  upper = c(NA, NA, lessagr$ulci)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -28L),
  class = "data.frame")


forestplot(lessagr2,
           graph.pos = 6,
           zero=1,
           rrslessagr,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:8), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           is.summary = c(T, T, F, 
                          T, F,
                          T, rep(F, 3), 
                          T, rep(F, 7), 
                          T, rep(F, 3), 
                          T, rep(F, 3), T, F, F),
           align = c("l","c", "c", "c", "l", "l", "l"),
           boxsize = 0.5,
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=1), 
                            ticks = gpar(cex = 1, fontface="bold"),
                            summary = gpar(cex = 1),
                            xlab = gpar(cex=0.9)),
           xticks = c(0.12, 0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(18,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))

```

> To generate this forest plot, we used information from Supplementary Figures 4 to 9.

</details>


### Figure 3
<details><summary>Click to show</summary>

*Risk of achieving Complete Stable Remission in patients with myasthenia gravis who underwent* ***Minimally Invasive Thymectomy***  *vs.* ***Minimally Invasive Thymectomy*** *at different follow-ups*


```{r,  fig.height=3, fig.width=15, echo=FALSE, message=FALSE, warning=FALSE}
less <- as_tibble(rbind(h, i))
colnames(less) <- head

less[,c(3:8,9:12)] <- sapply(less[,c(3:8,9:12)], as.numeric)
less$i2 <- ifelse(less$k==1, "na", paste(formatC(round2(less$i2,n=0), format='f',digits=0),"%"))
less$rr <- paste(formatC(round2(less$eff, n=2), format='f', digits=2), 
                "(", formatC(round2(less$llci, n=2), format='f', digits=2),
                "-", formatC(round2(less$ulci, n=2), format='f', digits=2),
                ")")
less$n1 <- (less$ai + less$bi)
less$n2 <- (less$ci + less$di)
less$rate1 <- paste(less$ai,"/",less$n1)
less$rate2 <- paste(less$ci,"/",less$n2)
less$p2 <- 
  ifelse(is.na(less$p), NA, 
  ifelse(less$p<0.001, paste("<0.001"), 
         paste(formatC(round2(less$p,n=3), format='f', digits=3))))



less <- less %>% add_row(followup="VATS extended lelft vs. VATS extended right", .before = 1)
less <- less %>% add_row(followup="VATS extended with robotic  vs. VATS extended", .before = 4)

less <- less %>% add_row(.before = 1)
less <- less %>% add_row(.after = 7)


less2 <- cbind(c("Treatment vs. Control", "Follow-up",less$followup),
              c("N of studies", NA, less$k),
              c("Treatment", "events/n", less$rate1),
              c("Control", "events/n", less$rate2),
              c("I^2", NA, less$i2),
              c("Relative Risk (95% CI)", NA, less$rr),
              c("p value", NA, less$p2))

sub1 <- c(5,6,8,9)
less2[,1][sub1] <- paste("  ",less2[,1][sub1])


rrsless <- structure(list(
  mean = c(NA, NA, less$eff),
  lower = c(NA, NA, less$llci),
  upper = c(NA, NA, less$ulci)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -10L),
  class = "data.frame")


forestplot(less2,
           graph.pos = 6,
           zero=1,
           rrsless,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:8), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           is.summary = c(T, T, F, 
                          T, rep(F, 2), 
                          T, rep(F,2), 
                          F),
           align = c("l","c", "c", "c", "l", "l", "l"),
           boxsize = 0.5,
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                            ticks = gpar(cex = 0.9, fontface="bold"),
                            summary = gpar(cex = 0.9),
                            xlab = gpar(cex=0.9)),
           xticks = c(0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(9,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))

```
</details>


### Figure 4
<details><summary>Click to show</summary>
*Risk of achieving Complete Stable Remission in patients with myasthenia gravis who underwent a* ***Minimally Invasive Thymectomy***  *those who underwent another* ***Minimally Invasive Thymectomy*** *at different follow-ups*

```{r label_of_this_figure,  fig.height=3, fig.width=14, echo=FALSE, message=FALSE, warning=FALSE}
less3 <- as_tibble(rbind(g))
colnames(less3) <- head

less3[,c(3:8,9:12)] <- sapply(less3[,c(3:8,9:12)], as.numeric)
less3$i2 <- ifelse(less3$k==1, "na", paste(formatC(round2(less3$i2,n=0), format='f',digits=0),"%"))
less3$rr <- paste(formatC(round2(less3$eff, n=2), format='f', digits=2), 
                "(", formatC(round2(less3$llci, n=2), format='f', digits=2),
                "-", formatC(round2(less3$ulci, n=2), format='f', digits=2),
                ")")
less3$n1 <- (less3$ai + less3$bi)
less3$n2 <- (less3$ci + less3$di)
less3$rate1 <- paste(less3$ai,"/",less3$n1)
less3$rate2 <- paste(less3$ci,"/",less3$n2)
less3$p2 <- 
  ifelse(is.na(less3$p), NA, 
  ifelse(less3$p<0.001, paste("<0.001"), 
         paste(formatC(round2(less3$p,n=3), format='f', digits=3))))



less3 <- less3 %>% add_row(followup="VATS extended uni vs. VATS extended bi", .before = 1)

less3 <- less3 %>% add_row(.before = 1)
less3 <- less3 %>% add_row(.after = 6)


less4 <- cbind(c("Treatment vs. Control", "Follow-up",less3$followup),
              c("N of studies", NA, less3$k),
              c("Treatment", "events/n", less3$rate1),
              c("Control", "events/n", less3$rate2),
              c("I^2", NA, less3$i2),
              c("Relative Risk (95% CI)", NA, less3$rr),
              c("p value", NA, less3$p2))

sub1 <- c(5:8)
less4[,1][sub1] <- paste("  ",less4[,1][sub1])


rrsless <- structure(list(
  mean = c(NA, NA, less3$eff),
  lower = c(NA, NA, less3$llci),
  upper = c(NA, NA, less3$ulci)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -9L),
  class = "data.frame")


forestplot(less4,
           graph.pos = 6,
           zero=1,
           rrsless,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:8), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           is.summary = c(T, T, F, 
                          T, rep(F, 4), 
                          F),
           align = c("l","c", "c", "c", "l", "l", "l"),
           boxsize = 0.5,
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.9), 
                            ticks = gpar(cex = 0.9, fontface="bold"),
                            summary = gpar(cex = 0.9),
                            xlab = gpar(cex=0.9)),
           xticks = c(0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(9,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))

```
</details>



## Supplementary Figures

### Extended Transsternal vs. Standard Transsternal forest plots
<details><summary> Suppl. Figure 1: Extended Transsternal vs. Standard Transsternal, risk of CSR at 3 years of follow-up </summary>
<p>

```{r forestplotma40, echo=FALSE, fig.height=3, fig.width=10, message=FALSE, warning=FALSE}
boxsize <- (0.0125*(weights(ma1)))

tfma1 <- cbind( 
  c( "Author", NA, prema1$author, 
     paste("Overall relative risk for", ma1$k.eff, "studies","\n", 
           "(Tau^2 = ", (formatC(ma1$tau2, digits=2, format="f")), 
           ", df = ", (ma1$k - ma1$p),
           "; ", "I^2", "= ", (formatC(ma1$I2, digits=1, format="f")),"%",
           ", p ", (ifelse(ma1$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(ma1$QEp, digits=3, format="f")))), 
            ")")),
  c( "T3b", "events/n", paste(prema1$events1,"/",prema1$n1), 
     paste(sum(prema1$events1, na.rm=TRUE),"/", sum(prema1$n1, na.rm=TRUE))),
  
  c( "T3a", "events/n", paste(prema1$events2,"/",prema1$n2), 
     paste(sum(prema1$events2, na.rm=TRUE),"/",sum(prema1$n2, na.rm=TRUE))),
  
  c( "Relative Risk (95% CI)", NA,  prema1$rr, 
     paste(formatC(expma1$pred, format='f', digits =2), 
           " (",formatC(expma1$ci.lb, format='f', digits=2),
           "-", formatC(expma1$ci.ub, format='f', digits=2), ")")))


tfma1 <- as_tibble(tfma1)
tfma1 <- add_row(tfma1, .after = 4)
tfma1 <- add_row(tfma1, .after = 6)


rrsma1 <- structure(list(
  mean = c(NA, NA,  exp(prema1$yi), NA, expma1$pred, NA),
  lower = c(NA, NA,  exp(prema1$ci.lb), NA,  expma1$ci.lb, NA),
  upper = c(NA, NA, exp(prema1$ci.ub), NA, expma1$ci.ub, NA)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -7L),
  class = "data.frame")


forestplot(tfma1,
           graph.pos = 4,
           zero=1,
           rrsma1,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:5), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           boxsize = c(NA, NA, boxsize, NA, 1,NA),
           is.summary = c(T, T, rep(F, 3), T, F),
           align = c("l","c", "c"),
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                            ticks = gpar(cex = 0.8, fontface="bold"),
                            summary = gpar(cex = 0.8),
                            xlab = gpar(cex=0.8)),
           xticks = c(0.12, 0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(7,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))
```
</p>
</details>


<details><summary> Suppl. Figure 2: Extended Transsternal vs. Standard Transsternal, risk of CSR at 4 years of follow-up </summary>
<p>

```{r forestplotma41, echo=FALSE, fig.height=3, fig.width=10, message=FALSE, warning=FALSE}
boxsize <- (0.0125*(weights(ma2)))

tfma2 <- cbind( 
  c( "Author", NA, prema2$author, 
     paste("Overall relative risk for", ma2$k.eff, "studies","\n", 
           "(Tau^2 = ", (formatC(ma2$tau2, digits=2, format="f")), 
           ", df = ", (ma2$k - ma2$p),
           "; ", "I^2", "= ", (formatC(ma2$I2, digits=1, format="f")),"%",
           ", p ", (ifelse(ma2$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(ma2$QEp, digits=3, format="f")))), 
            ")")),
  c( "T3b", "events/n", paste(prema2$events1,"/",prema2$n1), 
     paste(sum(prema2$events1, na.rm=TRUE),"/", sum(prema2$n1, na.rm=TRUE))),
  
  c( "T3a", "events/n", paste(prema2$events2,"/",prema2$n2), 
     paste(sum(prema2$events2, na.rm=TRUE),"/",sum(prema2$n2, na.rm=TRUE))),
  
  c( "Relative Risk (95% CI)", NA,  prema2$rr, 
     paste(formatC(expma2$pred, format='f', digits =2), 
           " (",formatC(expma2$ci.lb, format='f', digits=2),
           "-", formatC(expma2$ci.ub, format='f', digits=2), ")")))


tfma2 <- as_tibble(tfma2)
tfma2 <- add_row(tfma2, .after = 4)
tfma2 <- add_row(tfma2, .after = 6)


rrsma2 <- structure(list(
  mean = c(NA, NA,  exp(prema2$yi), NA, expma2$pred, NA),
  lower = c(NA, NA,  exp(prema2$ci.lb), NA,  expma2$ci.lb, NA),
  upper = c(NA, NA, exp(prema2$ci.ub), NA, expma2$ci.ub, NA)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -7L),
  class = "data.frame")


forestplot(tfma2,
           graph.pos = 4,
           zero=1,
           rrsma2,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:5), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           boxsize = c(NA, NA, boxsize, NA, 1,NA),
           is.summary = c(T, T, rep(F, 3), T, F),
           align = c("l","c", "c"),
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                            ticks = gpar(cex = 0.8, fontface="bold"),
                            summary = gpar(cex = 0.8),
                            xlab = gpar(cex=0.8)),
           xticks = c(0.12, 0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(7,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))
```
</p>
</details>



<details><summary> Suppl. Figure 3: Extended Transsternal vs. Standard Transsternal, risk of CSR at 4 years of follow-up </summary>
<p>

```{r forestplotma42, echo=FALSE, fig.height=3, fig.width=10, message=FALSE, warning=FALSE}
boxsize <- (0.0125*(weights(ma3)))

tfma3 <- cbind( 
  c( "Author", NA, prema3$author, 
     paste("Overall relative risk for", ma3$k.eff, "studies","\n", 
           "(Tau^2 = ", (formatC(ma3$tau2, digits=2, format="f")), 
           ", df = ", (ma3$k - ma3$p),
           "; ", "I^2", "= ", (formatC(ma3$I2, digits=1, format="f")),"%",
           ", p ", (ifelse(ma3$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(ma3$QEp, digits=3, format="f")))), 
            ")")),
  c( "T3b", "events/n", paste(prema3$events1,"/",prema3$n1), 
     paste(sum(prema3$events1, na.rm=TRUE),"/", sum(prema3$n1, na.rm=TRUE))),
  
  c( "T3a", "events/n", paste(prema3$events2,"/",prema3$n2), 
     paste(sum(prema3$events2, na.rm=TRUE),"/",sum(prema3$n2, na.rm=TRUE))),
  
  c( "Relative Risk (95% CI)", NA,  prema3$rr, 
     paste(formatC(expma3$pred, format='f', digits =2), 
           " (",formatC(expma3$ci.lb, format='f', digits=2),
           "-", formatC(expma3$ci.ub, format='f', digits=2), ")")))


tfma3 <- as_tibble(tfma3)
tfma3 <- add_row(tfma3, .after = 4)
tfma3 <- add_row(tfma3, .after = 6)


rrsma3 <- structure(list(
  mean = c(NA, NA,  exp(prema3$yi), NA, expma3$pred, NA),
  lower = c(NA, NA,  exp(prema3$ci.lb), NA,  expma3$ci.lb, NA),
  upper = c(NA, NA, exp(prema3$ci.ub), NA, expma3$ci.ub, NA)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -7L),
  class = "data.frame")


forestplot(tfma3,
           graph.pos = 4,
           zero=1,
           rrsma3,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:5), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           boxsize = c(NA, NA, boxsize, NA, 1,NA),
           is.summary = c(T, T, rep(F, 3), T, F),
           align = c("l","c", "c"),
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                            ticks = gpar(cex = 0.8, fontface="bold"),
                            summary = gpar(cex = 0.8),
                            xlab = gpar(cex=0.8)),
           xticks = c(0.12, 0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(7,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))
```
</p>
</details>



### Extended Transsternal vs. VATS extended forest plots
<details><summary> Suppl. Figure 4: Extended Transsternal vs. VATS extended, risk of CSR at 3 years of follow-up </summary>
<p>
```{r forestplotma43, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=9.5}
boxsize <- (0.01666667*(weights(ma8)))

tfma8 <- cbind( 
  c( "Author", NA, prema8$author, 
     paste("Overall relative risk for", ma8$k.eff, "studies","\n", 
           "(Tau^2 = ", (formatC(ma8$tau2, digits=2, format="f")), 
           ", df = ", (ma8$k - ma8$p),
           "; ", "I^2", "= ", (formatC(ma8$I2, digits=1, format="f")),"%",
           ", p ", (ifelse(ma8$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(ma8$QEp, digits=3, format="f")))), 
            ")")),
  c( "T3b", "events/n", paste(prema8$events1,"/",prema8$n1), 
     paste(sum(prema8$events1, na.rm=TRUE),"/", sum(prema8$n1, na.rm=TRUE))),
  
  c( "T2a", "events/n", paste(prema8$events2,"/",prema8$n2), 
     paste(sum(prema8$events2, na.rm=TRUE),"/",sum(prema8$n2, na.rm=TRUE))),
  
  c( "Relative Risk (95% CI)", NA,  prema8$rr, 
     paste(formatC(expma8$pred, format='f', digits =2), 
           " (",formatC(expma8$ci.lb, format='f', digits=2),
           "-", formatC(expma8$ci.ub, format='f', digits=2), ")")))

tfma8 <- as_tibble(tfma8)
tfma8 <- add_row(tfma8, .after = 8)
tfma8 <- add_row(tfma8, .after = 10)

rrsma8 <- structure(list(
  mean = c(NA, NA,  exp(prema8$yi), NA, expma8$pred, NA),
  lower = c(NA, NA,  exp(prema8$ci.lb), NA,  expma8$ci.lb, NA),
  upper = c(NA, NA, exp(prema8$ci.ub), NA, expma8$ci.ub, NA)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -11L),
  class = "data.frame")


forestplot(tfma8,
           graph.pos = 4,
           zero=1,
           rrsma8,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:5), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           boxsize = c(NA, NA, boxsize, NA, 1, NA),
           is.summary = c(T, T, rep(F, 7), T, F),
           align = c("l","c", "c"),
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                            ticks = gpar(cex = 0.8, fontface="bold"),
                            summary = gpar(cex = 0.8),
                            xlab = gpar(cex=0.8)),
           xticks = c(0.12, 0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(7,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))
```
</p>
</details>


<details><summary> Suppl. Figure 5: Extended Transsternal vs. VATS extended, risk of CSR at 4 years of follow-up </summary>
<p>
```{r forestplotma44, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=9.5}
boxsize <- (0.01666667*(weights(ma9)))

tfma9 <- cbind( 
  c( "Author", NA, prema9$author, 
     paste("Overall relative risk for", ma9$k.eff, "studies","\n", 
           "(Tau^2 = ", (formatC(ma9$tau2, digits=2, format="f")), 
           ", df = ", (ma9$k - ma9$p),
           "; ", "I^2", "= ", (formatC(ma9$I2, digits=1, format="f")),"%",
           ", p ", (ifelse(ma9$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(ma9$QEp, digits=3, format="f")))), 
            ")")),
  c( "T3b", "events/n", paste(prema9$events1,"/",prema9$n1), 
     paste(sum(prema9$events1, na.rm=TRUE),"/", sum(prema9$n1, na.rm=TRUE))),
  
  c( "T2b", "events/n", paste(prema9$events2,"/",prema9$n2), 
     paste(sum(prema9$events2, na.rm=TRUE),"/",sum(prema9$n2, na.rm=TRUE))),
  
  c( "Relative Risk (95% CI)", NA,  prema9$rr, 
     paste(formatC(expma9$pred, format='f', digits =2), 
           " (",formatC(expma9$ci.lb, format='f', digits=2),
           "-", formatC(expma9$ci.ub, format='f', digits=2), ")")))

tfma9 <- as_tibble(tfma9)
tfma9 <- add_row(tfma9, .after = 8)
tfma9 <- add_row(tfma9, .after = 10)

rrsma9 <- structure(list(
  mean = c(NA, NA,  exp(prema9$yi), NA, expma9$pred, NA),
  lower = c(NA, NA,  exp(prema9$ci.lb), NA,  expma9$ci.lb, NA),
  upper = c(NA, NA, exp(prema9$ci.ub), NA, expma9$ci.ub, NA)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -11L),
  class = "data.frame")

forestplot(tfma9,
           graph.pos = 4,
           zero=1,
           rrsma9,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:5), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           boxsize = c(NA, NA, boxsize, NA, 1, NA),
           is.summary = c(T, T, rep(F, 7), T, F),
           align = c("l","c", "c"),
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                            ticks = gpar(cex = 0.8, fontface="bold"),
                            summary = gpar(cex = 0.8),
                            xlab = gpar(cex=0.8)),
           xticks = c(0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(7,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))

```
</p>
</details>



<details><summary> Suppl. Figure 6: Extended Transsternal vs. VATS extended, risk of CSR at 5 years of follow-up </summary>
<p>
```{r forestplotma45, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=9.5}
boxsize <- (0.0125*(weights(ma10)))

tfma10 <- cbind( 
  c( "Author", NA, prema10$author, 
     paste("Overall relative risk for", ma10$k.eff, "studies","\n", 
           "(Tau^2 = ", (formatC(ma10$tau2, digits=2, format="f")), 
           ", df = ", (ma10$k - ma10$p),
           "; ", "I^2", "= ", (formatC(ma10$I2, digits=1, format="f")),"%",
           ", p ", (ifelse(ma10$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(ma10$QEp, digits=3, format="f")))), 
            ")")),
  c( "T3b", "events/n", paste(prema10$events1,"/",prema10$n1), 
     paste(sum(prema10$events1, na.rm=TRUE),"/", sum(prema10$n1, na.rm=TRUE))),
  
  c( "T2a", "events/n", paste(prema10$events2,"/",prema10$n2), 
     paste(sum(prema10$events2, na.rm=TRUE),"/",sum(prema10$n2, na.rm=TRUE))),
  
  c( "Relative Risk (95% CI)", NA,  prema10$rr, 
     paste(formatC(expma10$pred, format='f', digits =2), 
           " (",formatC(expma10$ci.lb, format='f', digits=2),
           "-", formatC(expma10$ci.ub, format='f', digits=2), ")")))

tfma10 <- as_tibble(tfma10)
tfma10 <- add_row(tfma10, .after = 7)
tfma10 <- add_row(tfma10, .after = 9)

rrsma10 <- structure(list(
  mean = c(NA, NA,  exp(prema10$yi), NA, expma10$pred, NA),
  lower = c(NA, NA,  exp(prema10$ci.lb), NA,  expma10$ci.lb, NA),
  upper = c(NA, NA, exp(prema10$ci.ub), NA, expma10$ci.ub, NA)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -10L),
  class = "data.frame")

forestplot(tfma10,
           graph.pos = 4,
           zero=1,
           rrsma10,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:5), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           boxsize = c(NA, NA, boxsize, NA, 1, NA),
           is.summary = c(T, T, rep(F, 6), T, F),
           align = c("l","c", "c"),
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                            ticks = gpar(cex = 0.8, fontface="bold"),
                            summary = gpar(cex = 0.8),
                            xlab = gpar(cex=0.8)),
           xticks = c(0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(7,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))
```
</p>
</details>


<details><summary> Suppl. Figure 7: Extended Transsternal vs. VATS extended, risk of CSR at 6 years of follow-up </summary>
<p>
```{r forestplotma46, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=9.5}
boxsize <- (0.0125*(weights(ma11)))

tfma11 <- cbind( 
  c( "Author", NA, prema11$author, 
     paste("Overall relative risk for", ma11$k.eff, "studies","\n", 
           "(Tau^2 = ", (formatC(ma11$tau2, digits=2, format="f")), 
           ", df = ", (ma11$k - ma11$p),
           "; ", "I^2", "= ", (formatC(ma11$I2, digits=1, format="f")),"%",
           ", p ", (ifelse(ma11$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(ma11$QEp, digits=3, format="f")))), 
            ")")),
  c( "T3b", "events/n", paste(prema11$events1,"/",prema11$n1), 
     paste(sum(prema11$events1, na.rm=TRUE),"/", sum(prema11$n1, na.rm=TRUE))),
  
  c( "T2a", "events/n", paste(prema11$events2,"/",prema11$n2), 
     paste(sum(prema11$events2, na.rm=TRUE),"/",sum(prema11$n2, na.rm=TRUE))),
  
  c( "Relative Risk (95% CI)", NA,  prema11$rr, 
     paste(formatC(expma11$pred, format='f', digits =2), 
           " (",formatC(expma11$ci.lb, format='f', digits=2),
           "-", formatC(expma11$ci.ub, format='f', digits=2), ")")))

tfma11 <- as_tibble(tfma11)
tfma11 <- add_row(tfma11, .after = 6)
tfma11 <- add_row(tfma11, .after = 8)

rrsma11 <- structure(list(
  mean = c(NA, NA,  exp(prema11$yi), NA, expma11$pred, NA),
  lower = c(NA, NA,  exp(prema11$ci.lb), NA,  expma11$ci.lb, NA),
  upper = c(NA, NA, exp(prema11$ci.ub), NA, expma11$ci.ub, NA)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -9L),
  class = "data.frame")

forestplot(tfma11,
           graph.pos = 4,
           zero=1,
           rrsma11,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:5), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           boxsize = c(NA, NA, boxsize, NA, 1, NA),
           is.summary = c(T, T, rep(F, 5), T, F),
           align = c("l","c", "c"),
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                            ticks = gpar(cex = 0.8, fontface="bold"),
                            summary = gpar(cex = 0.8),
                            xlab = gpar(cex=0.8)),
           xticks = c(0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(7,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))
```
</p>
</details>

<details><summary> Suppl. Figure 8: Extended Transsternal vs. VATS extended, risk of CSR at 7 years of follow-up </summary>
<p>
```{r forestplotma47, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=9.5}
boxsize <- (0.0125*(weights(ma12)))

tfma12 <- cbind( 
  c( "Author", NA, prema12$author, 
     paste("Overall relative risk for", ma12$k.eff, "studies","\n", 
           "(Tau^2 = ", (formatC(ma12$tau2, digits=2, format="f")), 
           ", df = ", (ma12$k - ma12$p),
           "; ", "I^2", "= ", (formatC(ma12$I2, digits=1, format="f")),"%",
           ", p ", (ifelse(ma12$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(ma12$QEp, digits=3, format="f")))), 
            ")")),
  c( "T3b", "events/n", paste(prema12$events1,"/",prema12$n1), 
     paste(sum(prema12$events1, na.rm=TRUE),"/", sum(prema12$n1, na.rm=TRUE))),
  
  c( "T2a", "events/n", paste(prema12$events2,"/",prema12$n2), 
     paste(sum(prema12$events2, na.rm=TRUE),"/",sum(prema12$n2, na.rm=TRUE))),
  
  c( "Relative Risk (95% CI)", NA,  prema12$rr, 
     paste(formatC(expma12$pred, format='f', digits =2), 
           " (",formatC(expma12$ci.lb, format='f', digits=2),
           "-", formatC(expma12$ci.ub, format='f', digits=2), ")")))

tfma12 <- as_tibble(tfma12)
tfma12 <- add_row(tfma12, .after = 6)
tfma12 <- add_row(tfma12, .after = 8)

rrsma12 <- structure(list(
  mean = c(NA, NA,  exp(prema12$yi), NA, expma12$pred, NA),
  lower = c(NA, NA,  exp(prema12$ci.lb), NA,  expma12$ci.lb, NA),
  upper = c(NA, NA, exp(prema12$ci.ub), NA, expma12$ci.ub, NA)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -9L),
  class = "data.frame")

forestplot(tfma12,
           graph.pos = 4,
           zero=1,
           rrsma12,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:5), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           boxsize = c(NA, NA, boxsize, NA, 1, NA),
           is.summary = c(T, T, rep(F, 5), T, F),
           align = c("l","c", "c"),
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                            ticks = gpar(cex = 0.8, fontface="bold"),
                            summary = gpar(cex = 0.8),
                            xlab = gpar(cex=0.8)),
           xticks = c(0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(7,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))
```
</p>
</details>


<details><summary> Suppl. Figure 9: Extended Transsternal vs. VATS extended, risk of CSR at 8 years of follow-up </summary>
<p>
```{r forestplotma48, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=9.5}
boxsize <- (0.0125*(weights(ma13)))

tfma13 <- cbind( 
  c( "Author", NA, prema13$author, 
     paste("Overall relative risk for", ma13$k.eff, "studies","\n", 
           "(Tau^2 = ", (formatC(ma13$tau2, digits=2, format="f")), 
           ", df = ", (ma13$k - ma13$p),
           "; ", "I^2", "= ", (formatC(ma13$I2, digits=1, format="f")),"%",
           ", p ", (ifelse(ma13$QEp < 0.001, 
                           paste("< 0.001"),
                           paste("= ", formatC(ma13$QEp, digits=3, format="f")))), 
            ")")),
  c( "VATS uni", "events/n", paste(prema13$events1,"/",prema13$n1), 
     paste(sum(prema13$events1, na.rm=TRUE),"/", sum(prema13$n1, na.rm=TRUE))),
  
  c( "ETsT", "events/n", paste(prema13$events2,"/",prema13$n2), 
     paste(sum(prema13$events2, na.rm=TRUE),"/",sum(prema13$n2, na.rm=TRUE))),
  
  c( "Relative Risk (95% CI)", NA,  prema13$rr, 
     paste(formatC(expma13$pred, format='f', digits =2), 
           " (",formatC(expma13$ci.lb, format='f', digits=2),
           "-", formatC(expma13$ci.ub, format='f', digits=2), ")")))

tfma13 <- as_tibble(tfma13)
tfma13 <- add_row(tfma13, .after = 5)
tfma13 <- add_row(tfma13, .after = 7)

rrsma13 <- structure(list(
  mean = c(NA, NA,  exp(prema13$yi), NA, expma13$pred, NA),
  lower = c(NA, NA,  exp(prema13$ci.lb), NA,  expma13$ci.lb, NA),
  upper = c(NA, NA, exp(prema13$ci.ub), NA, expma13$ci.ub, NA)),
  .Names = c("mean", "lower", "upper"),
  row.names = c(NA, -8L),
  class = "data.frame")

forestplot(tfma13,
           graph.pos = 4,
           zero=1,
           rrsma13,
           new_page = TRUE,
           colgap = unit(5, "mm"),
           hrzl_lines = list("3" = gpar (lwd=1, columns=c(1:5), col="black") 
           ),
           lineheight=unit(0.6,'cm'),
           line.margin = 2,
           boxsize = c(NA, NA, boxsize, NA, 1, NA),
           is.summary = c(T, T, rep(F, 4), T, F),
           align = c("l","c", "c"),
           ci.vertices = TRUE,
           txt_gp = fpTxtGp(label =gpar (cex=0.8), 
                            ticks = gpar(cex = 0.8, fontface="bold"),
                            summary = gpar(cex = 0.8),
                            xlab = gpar(cex=0.8)),
           xticks = c(0.25, 0.5, 1, 2, 4, 8),
           xlog=TRUE,
           clip = c(0.5, 4),
           lwd.xaxis = 1,
           lwd.ci = 2.2,
           graphwidth = unit(7,"cm"),
           col=fpColors(box="black",line="grey", 
                        axes="grey20", summary="black", zero="black"))
```
</p>
</details>

